\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}

\setlist[itemize]{topsep=4pt,itemsep=3pt}
\setlist[enumerate]{topsep=4pt,itemsep=3pt}

\title{Final Project --- Submission Guidelines}
\author{}
\date{}

\begin{document}

\maketitle


\section*{What I want from you}

\begin{enumerate}
    \item \textbf{Code} --- a working Python script or notebook implementing your method.
    \item \textbf{Presentation} --- a short write-up / slide deck covering motivation, method, validation results, and what did not work. Cross-validation is required wherever it applies; numbers without out-of-sample evaluation are not evidence.
\end{enumerate}

Deadline: both the code and the presentation must be sent to me via email at least 48 hours before your presentation datetime.

\section*{Project 2}

\begin{itemize}

    \item \textbf{Trade-side classification.} Given trade prices and volumes, with no quotes, infer the aggressor side of each print. Beat or motivate beyond Lee--Ready / tick rule / quote rule baselines.

\end{itemize}

\section*{Code interface for the structured projects}

For Project 2, wrap your method as a single class or function with a clean signature. I should be able to import it and run it on my own data.

\subsection*{Project 2}

\begin{verbatim}
def classify_side(
    trades: pd.DataFrame
) -> pd.Series:
\end{verbatim}

Input is a pandas DataFrame with trade price and volume columns, time-indexed. Output is a boolean pandas Series aligned to the input where \texttt{True} means sell aggressor and \texttt{False} means buy aggressor, matching the convention of the sample data.

\section*{Sample data}

Exemplary crypto trades and order-book data is attached for you to develop and validate against. Conventions:

\begin{itemize}
    \item Trades: the aggressor-side flag is boolean --- \texttt{True} means sell aggressor, \texttt{False} means buy aggressor.
    \item Order books: standard L2 snapshots, with bids and asks including prices and sizes.
\end{itemize}


\end{document}